### 2022-02-13 thesis.tex
commentaires du patron

\begin{document}
\frontmatter
  \input{include/title}
  \clearemptydoublepage
  \input{include/abstract}
  %\clearemptydoublepage
  \input{include/thanks}
  \clearemptydoublepage
  \tableofcontents
  \clearemptydoublepage
  % \input{include/glossary}
  % \clearemptydoublepage
  \mainmatter 
%%%%
\mychapter{Introduction} \label{chap:intro}
 \input{chapters/intro/intro}    
%%
%%%%%% 
\mychapter{Modeling the spread of SCTLD in Florida} \label{chap:sctld}
\chaptermark{Modeling the spread of SCTLD in Florida}  
\input{chapters/sctld/sctld}
\mychapter{Transmission of SCTLD from the Marquesas to the Dry Tortugas}\label{chap:drto}
\chaptermark{Transmission of SCTLD from the Marquesas to the DRTO}  
\input{chapters/drto/drto}
\mychapter{The onset of the SCTLD outbreak and the PortMiami Deep Dredge Project} \label{chap:onset}
\chaptermark{Onset of SCTLD and PortMiami Deep Dredge Project}  
\input{chapters/onset/onset}
\mychapter{Impacts of hurricanes on wave-induced ocean transport processes} \label{chap:irma}
\chaptermark{Wave-induced transport under hurricanes}  
\input{chapters/irma/irma}
%%%%%%%%%%%
%
%%%%%  
%%%
  \mychapter{Conclusions and perspectives} \label{chap:conclusion}
  \input{chapters/conclusions/conclusions}    
%%
%
  \clearemptydoublepage
  \bibliography{include/bibliography.bib}

>>>>

\begin{document}
\frontmatter
  \input{include/title}
  \clearemptydoublepage
  \input{include/abstract}
  \clearemptydoublepage
  %\input{include/thanks}
  %\clearemptydoublepage
  \tableofcontents
  \clearemptydoublepage
  % \input{include/glossary}
  % \clearemptydoublepage
  \mainmatter 
%%%%
\mychapter{Introduction} \label{chap:intro}
 \input{chapters/intro/intro}    
%%
%%%%%% 
\mychapter{Processes driving the spread of SCTLD through the FRT} \label{chap:sctld}
\chaptermark{Processes driving the spread of SCTLD in the FRT}  
\input{chapters/sctld/sctld}
\mychapter{Transmission dynamics of SCTLD from the Marquesas and to the DRTO}\label{chap:drto}
\chaptermark{Transmission of SCTLD from the Marquesas to the DRTO}  
\input{chapters/drto/drto}
\mychapter{The onset of the SCTLD outbreak and the PortMiami Deep Dredge Project} \label{chap:onset}
\chaptermark{Onset of SCTLD and PortMiami Deep Dredge Project}  
\input{chapters/onset/onset}
\mychapter{Impacts of hurricanes on transport processes in the Florida Keys} \label{chap:irma}
\chaptermark{Wave-induced transport under hurricanes}  
\input{chapters/irma/irma}
%%%%%%%%%%%
%
%%%%%  
%%%
  \mychapter{Conclusions and perspectives} \label{chap:conclusion}
  \input{chapters/conclusions/conclusions}    
%%
%
  \clearemptydoublepage
  \bibliography{include/bibliography.bib}
